---
title: "Palmer Penguins Initial Analysis"
author: "Kati Lebor"
format: html
editor: visual
execute:
  keep-md: true
---

# *Palmer Penguins*

This is an analysis of the Palmer Penguin dataset

```{r}
library(tidyverse)
library(kableExtra)

#Read the penguins_samp1 data file from github
penguins <- read_csv("https://raw.githubusercontent.com/mcduryea/Intro-to-Bioinformatics/main/data/penguins_samp1.csv")

#See the first six rows of the data we've read in to our notebook
penguins %>%
  head(2) %>%
  kable() %>%
  kable_styling(c("striped", "hover"))
  

 
```

## Data Manipulation

Including a narrative alongside any analysis is extremely important. It is difficult for someone to simply read your code and immediately know what you are doing. Walking a reader through your thought process is helpful. As a reminder, Quarto notebooks allow you to mix R-code and text -- in general, code chunks appear with a grey background while text appears over a white background.

Write a few sentences below the header to remind yourself that we\'ll be learning how to use R code to manipulate data in this section. In particular, we\'ll learn how to filter rows, subset columns, group data, and compute summary statistics.

Questions:

1.) Does the island that a Gentoo penguin live on impact the length of the bill?

2.) What is the average flipper length of all male species of penguins?

3.) What is the the average bill depth of all female penguins?

```{r}
penguins %>%
  count(island)

  

```
